The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free eLearning program CrypTool\\ (9th edition -- distributed with CrypTool version 1.4.20)} \vspace{60pt}

### 2009-06-30 script/en/script-en.tex
Add GNU FDL version 1.3 as the license for this script

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{ 
	The CrypTool Script: \\
	Cryptography, Mathematics and more \\
        \vspace{30pt}
        {\large	Background reading\\%*[-8pt] 
        for the free eLearning program CrypTool\\
       (9th edition -- distributed with CrypTool version 1.4.20)}
        \vspace{60pt}
}

@@

\author{
(c) Prof.\ Bernhard Esslinger (co-author and editor), 1998-2008 \\
Frankfurt am Main, Germany\\*[1ex]
www.cryptool.org
}

@@

% Vergleichbar zur Nutzung von Texten aus der Wikipedia (=GNU Free Documentation Licence, GFDL)
\vspace{200pt}
This is a free document, so the content of the document can be copied and
distributed, also for commercial purposes -- as long as the author, title and
the CrypTool web site (www.cryptool.org) are acknowledged. \\
Naturally, citations from the CrypTool script are possible, as in all other
documents. This licence is abutted on the GNU Free Documentation Licence.

@@

\begin{appendix}
  \newpage
  \input{chapters/menus.tex}
  \input{chapters/authors.tex}
\end{appendix}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{ 
	The CrypTool Script: \\
	Cryptography, Mathematics and More \\
        \vspace{30pt}
        {\large	Background reading\\%*[-8pt] 
        for the free eLearning program CrypTool\\
       (9th edition -- distributed with CrypTool version 1.4.20)}
        \vspace{60pt}
}

@@

\author{
Copyright (c) Prof.\ Bernhard Esslinger (co-author and editor) \\
and the CrypTool Development Team, 1998-2008 \\
Frankfurt am Main, Germany\\*[1ex]
\url{www.cryptool.org}
}

@@

% Vergleichbar zur Nutzung von Texten aus der Wikipedia (=GNU Free Documentation Licence, GFDL)
% \vspace{200pt}
\newpage
\noindent This is a free document, so the content of the document can
be copied and distributed, also for commercial purposes --- as long as
the authors, title and the CrypTool web site (\url{www.cryptool.org})
are acknowledged. Naturally, citations from the CrypTool script are
possible, as in all other documents. The specific license for this
document is the GNU Free Documentation Licence.

\begin{quote}
    Copyright \copyright{} 1998--2009 Bernhard Esslinger and the
    CrypTool Development Team. Permission is granted to copy,
    distribute and/or modify this document under the terms of the GNU
    Free Documentation License, Version 1.3 or any later version
    published by the Free Software Foundation; with no Invariant
    Sections, no Front-Cover Texts, and no Back-Cover Texts. A copy of
    the license is included in the section entitled ``GNU Free
    Documentation License''.
\end{quote}

@@

\begin{appendix}
  \newpage
  \input{chapters/menus.tex}
  \input{chapters/authors.tex}
  \input{chapters/gnu-fdl-1.3.tex}
\end{appendix}
